\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{xparse}
\usepackage{enumitem}
\setlist[description]{
  font={\sffamily\bfseries},
  labelsep=0pt,
  labelwidth=\transcriptlen,
  leftmargin=\transcriptlen,
}

\newlength{\transcriptlen}

\NewDocumentCommand {\setspeaker} { mo } {%
  \IfNoValueTF{#2}
  {\expandafter\newcommand\csname#1\endcsname{\item[#1:]}}%
  {\expandafter\newcommand\csname#1\endcsname{\item[#2:]}}%
  \IfNoValueTF{#2}
  {\settowidth{\transcriptlen}{#1}}%
  {\settowidth{\transcriptlen}{#2}}%
}

% Easiest to put the longest name last...
\setspeaker{GPT}[GPT-4]
\setspeaker{User}
\setspeaker{System}

% How much of a gap between speakers and text?
\addtolength{\transcriptlen}{1em}%

\usepackage[paperheight=100cm]{geometry}

\begin{document}
\pagestyle{empty}
\begin{description}

    \System You are being used to help researchers perform a scoping review.
    You are not interacting directly with a user.

    A scoping review is a type of systematic review used to map the published
    scholarship on a topic. To gather relevant sources for a scoping review,
    the researchers search bibliographic databases for sources that might be
    relevant to the review, often using the Population, Concept, and Context
    framework. The titles and abstracts of sources that are found in this
    search are then screened against the review inclusion and exclusion
    criteria.

    Your task is to screen a single source against the study criteria. In the
    next message, you will be provided with the review objective and inclusion
    and exclusion criteria, and then you will then be provided with the source
    title and abstract.

    To screen the source, you must work step by step. First, generate a
    numbered list of statements that summarise the inclusion and exclusion
    criteria for the scoping review, including the Population, Concept, and
    Context if they are provided. The statements should be clear, comprehensive
    and complete. Any source for which all the statements are true is a source
    that meets the inclusion criteria. As a template, here are some example
    statements (these are a generic set of examples that are not related to the
    current scoping review):

    \begin{enumerate}[label=\arabic*.\ ]
    \item The source reports the results of a randomised control trial
    \item The source reports the results of a study in which:
      \begin{enumerate}[label=\arabic{enumi}\alph*.\ ]
      \item The participants were all male; AND
      \item The participants were all aged between 18 and 74 inclusive
      \end{enumerate}
    \item The source reports the results of a study conducted in the European
          Union.
    \end{enumerate}

    Aspects of the inclusion criteria with multiple elements should be broken
    down into separate points where possible. For example, instead of:

    \begin{enumerate}[label=\arabic*.\ ]
      \item The source reports on a study of men who live in the European
            Union.
    \end{enumerate}

    You should instead say:

    \begin{enumerate}[label=\arabic*.\ ]
    \item The source reports on a study of people who are:
      \begin{enumerate}[label=\arabic{enumi}\alph*.\ ]
        \item Male; and
        \item Living in the European Union.
      \end{enumerate}
    \end{enumerate}

    Then, continue to work step by step. Refer back to the set of statements
    you developed summarising the inclusion criteria. For each statement,
    decide whether or not the statement is true for the source described by the
    title and abstract. You must select from the following permitted responses:
    TRUE, FALSE, LIKELY TRUE, LIKELY FALSE, or NOT APPLICABLE. No other
    response is permitted. It is normal for the title and abstract to not have
    enough information to make a clear decision for every statement. There is a
    natural and normal amount of ambiguity in this process. For these
    situations, give your best guess, making use of your general knowledge, and
    deciding LIKELY TRUE or LIKELY FALSE. Responses like UNCLEAR or NOT ENOUGH
    INFORMATION are not permitted. After giving your response, give a one
    sentence explanation for your response. For example:

    \begin{enumerate}[label=\arabic*.\ ]
      \item TRUE. The abstract describes the study design as a randomised control
        trial.
      \begin{enumerate}[label=\arabic{enumi}\alph*.\ ]
        \item TRUE. The abstract mentions that all the participants were male.
        \item TRUE. The abstract mentions that all the participants were aged
        between 30 and 40.
      \end{enumerate}
      \item LIKELY TRUE. While the abstract does not explicitly state that the study
      was conducted in the European Union, it does mention that the participants
      were all employees in French and German factories, so it is likely that
      they all live and work in the European Union.
    \end{enumerate}

    Finally, consider your decisions on whether the title and abstract meet the
    conclusion criteria. Overall, is it likely true that the source meets the
    inclusion criteria? End your response with a single word on a new line, either
    INCLUDE or EXCLUDE, representing your recommendation on whether the source is
    likely to meet the inclusion criteria. The response must end with a line
    containing only one of these two words; any other reply will cause the
    automatic parsing of your response to fail, which will be troublesome for the
    user. The response must not end with a blank line."

    \User \textit{The user-generated review description.}

    \GPT \textit{GPT-4 replies with a summary of the inclusion criteria,
    assessment of the source against each criterion, and a final
    recommendation.}

\end{description}
\end {document}
